environmental_data_preperation

### 2018-11-27 src/env_data_prep.Rmd
simple plots complete

 NA values are represented by -99.99. Change these to NA
```{r}
naoraw <- replace(naoraw,naoraw==-99.99, NA)
```

@@

```{r}
nao <- naoraw[naoraw$year >= 1996, ]
head(nao) 
```

@@

```{r}
naocolumn <- matrix(t(amoraw[ ,2:13]), ncol=1) #month data is in col 2 - 13
naocolumn1 <- as.vector(naocolumn)
naotimeseries <- ts(naocolumn1, frequency = 12, start = c(1996,1))
plot.ts(naotimeseries)
abline(h = 0)
dev.copy(png, "../output/env/nao.png") #this prints a png of the plot
dev.off() #this turns off the print command
```

>>>>

 NA values are represented by -999. Change these to NA
```{r}
naoraw <- replace(naoraw,naoraw==-999, NA)
```

@@

```{r}
nao <- naoraw[naoraw$year >= 1996, ]
head(nao) 
summary(nao)
```

@@

```{r}
naocolumn <- matrix(t(nao[ ,2:13]), ncol=1) #month data is in col 2 - 13 
naocolumn1 <- as.vector(naocolumn)
naotimeseries <- ts(naocolumn1, frequency = 12, start = c(1996,1))
plot.ts(naotimeseries)
abline(h = 0)
dev.copy(png, "../output/env/nao.png") #this prints a png of the plot
dev.off() #this turns off the print command
```
